\SdM{Gaia identifies VFTS682 as the most massive, dynamically ejected runaway star known to date}

### 2018-05-11 VFTS682.tex
very first abstract

\thanks{M.~Renzo, \href{mailto:m.renzo@uva.nl}{m.renzo@uva.nl}}
\date{}
\begin{abstract}
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
\end{abstract}

@@

% make sure to cite this in the conclusion \cite{fujii:11, banerjee:12}

>>>>

\thanks{M.~Renzo, \href{mailto:m.renzo@uva.nl}{m.renzo@uva.nl}}
\date{}
\begin{abstract}
\SdM{ The formation and fates of the most massive stars remains one of the most elusive questions in stellar astrophysics. 
%
Previous work spectroscopic work identified VFTS682 as one of the most massive stars known. It resides in the field of the 30 Dor region in the Large Magellanic Cloud at a projected distance of 32 pc of the star cluster R136. The lack of a detected offset in radial velocity derived from the spectra, lead to speculations whether such extreme stars can form in relative isolation. 
%
We use Gaia's unprecedented proper motion measurements to investigate the kinematics of this object. We show that VFTS 682 is a bonafide runaway star moving with a relative velocity of about $60\kms$ away from the star cluster R136.  The inferred age, distance, and the magnitude and direction of the velocity are consistent a dynamical ejection scenario from the cluster. 
%
If correct, this would make VFTS 682 the most massive dynamically ejected runaway star known to date.  It proves that star clusters are capable of ejecting their most massive members. We discuss the implications for the existence of stars with masses well above the canonical upper mass limit inside the cluster, the internal dynamics in dense star clusters and the final fate of this object. }

\end{abstract}

@@

\todo{(1. Make sure we cite and disucss fujii:11, banerjee:12 in discussion. 2. Make link to dynamical interaction proposed to form BHBH systems. }
